---
title: "Customize boxes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Customize-boxes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hugodownplus)
```

# Heading

Text goes here


This alone will just render an expandable box using the `<details>` and `<summary>` HTML tags. All the formatting that we may want to apply has to happen in CSS.es can be used for the info-box:

```{css, eval = FALSE}
.note {
  /* customize the whole box */
}

summary.note-header,
.note-header {
  /* customize the box header */
}

.note-details {
  /* customize the content of the box */
}
```

Note that the class inside the fenced (pandoc) div `:::` is called `.info-box`, but the CSS classes are called `.note`. This is because `info` is a very common class which is why the CSS selectors take `.note` as class instead.

Similarly, the CSS selectors for the warn box look like this:

```{css, eval = FALSE}
.warn {
  /* customize the whole box */
}

summary.warn-header,
.warn-header {
  /* customize the box header */
}

.warn-details {
  /* customize the content of the box */
}
```
